%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdfusetitle,hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}

\usepackage{fontawesome5}   % for icons
\usepackage{ifthen}     

%----------FONT OPTIONS----------
% Font options
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)

\definecolor{zinc600}{RGB}{82,82,91}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \\[2pt]
      \footnotesize#2 & \\[4pt]
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\scriptsize$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt, topsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

% Fix external-link icons in \href
\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{#2 \raisebox{.15ex}{\footnotesize \faExternalLink*}}}

\renewcommand{\baselinestretch}{1.05}
\setlength{\parskip}{0pt}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\headerfontiii

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Umesh Tiruvalluru} \\ \vspace{2pt}
    {\color{zinc600}\textbf{Full Stack Developer}} \\[6pt]    

    \normalsize
    \mbox{{\footnotesize\faMapMarker*}\hspace*{0.13cm}Nellore, Andhra Pradesh}%
    \kern 0.5 cm%
    \mbox{\hrefWithoutArrow{mailto:tiruvalluruumesh@gmail.com}{{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}tiruvalluruumesh@gmail.com}}%
    \kern 0.5 cm%
    \mbox{\hrefWithoutArrow{tel:+91-834-186-48-14}{{\footnotesize\faPhone*}\hspace*{0.13cm}+91 83418 64814}}%
    \\[4pt] % <-- vertical gap before next row
    \mbox{\hrefWithoutArrow{https://www.umesh.tech/}{{\footnotesize\faLink}\hspace*{0.13cm}umesh.tech}}%
    \kern 0.5 cm%
    \mbox{\hrefWithoutArrow{https://linkedin.com/in/umeshTiruvalluru}{{\footnotesize\faLinkedinIn}\hspace*{0.13cm}umeshTiruvalluru}}%
    \kern 0.5 cm%
    \mbox{\hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru}{{\footnotesize\faGithub}\hspace*{0.13cm}Umesh-Tiruvalluru}}%

\end{center}

%-----------PROFESSIONAL SUMMARY-----------
% \section{Professional Summary}
% \resumeItemListStart
%   \resumeItem{Full Stack Developer skilled in creating scalable web applications with React, Next.js, and Node.js. Experienced with PostgreSQL and MongoDB databases. Proficient in RESTful API development, authentication systems, and performance optimization. Knowledgeable in CI/CD pipelines, and version control. Background in database design, AWS cloud deployment, and Docker containerization. Track record of delivering quality software and collaborating with cross-functional teams.}
% \resumeItemListEnd
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
      {AfterQuery}{Remote}
      {Software Engineer — Bash/Linux (Contract)}{September 30, 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Contributing to \textbf{Project Pluto}, developing realistic terminal-based tasks to evaluate frontier LLMs as part of AfterQuery's dataset initiative.}
        \resumeItem{Authored and submitted \textbf{5} end-to-end Terminal-Bench tasks; each task passed \textbf{11/11} validation checks required by the platform.}
        \resumeItem{Designed tasks to target medium–hard difficulty; observed LLM agent pass rates of \textbf{1 $–$ 4/10}, aligning with the project's targeted challenge distribution.}
        \resumeItem{Validated reproducibility and quality by pinning dependencies, providing deterministic tests, and preparing Docker-based environments; executed Oracle and Null agent validations locally.}
      \resumeItemListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{CozyStay} $-$ \hrefWithoutArrow{https://cozystay.umesh.tech}{\underline{Demo}} $|$ \hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru/cozystay}{\underline{Code}} }{\textbf{Tools:} Golang, PostgreSQL, Chi Router, Next.js, TypeScript, Tailwind CSS, Shadcn UI, Docker, JWT, REST API, AWS EC2, GitHub Actions}
          \resumeItemListStart
            \resumeItem{Developed full-stack property booking platform using Go, Next.js, and TypeScript. Created scalable RESTful APIs with Chi router and JWT authentication.}
            \resumeItem{Designed role-based access control (RBAC) with PostgreSQL. Established admin-only endpoints and secured sensitive operations using middleware authentication.}
            \resumeItem{Optimized Dockerfiles with multi-stage builds for backend and frontend. Reduced image sizes by 45\% and enhanced startup times by 35\%.}
            \resumeItem{Configured automated GitHub Actions CI/CD pipeline for Docker builds and AWS EC2 deployment. Cut manual deployment time by 60\%.}
            \resumeItem{Created booking system with dynamic search, real-time availability checks, automated pricing, and cancellation workflows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{LinkBrain} $-$ \hrefWithoutArrow{https://linkbrain.onrender.com}{\underline{Demo}} $|$ \hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru/LinkBrain}{\underline{Code}} }{\textbf{Tools:} React.js, Tailwind CSS, Express.js, MongoDB, Node.js, JWT, REST API}
          \resumeItemListStart
            \resumeItem{Created full-stack MERN application for organizing resources with user authentication.}
            \resumeItem{Designed secure authentication using JWT tokens and bcrypt password hashing. Secured user actions and API endpoints with proper session management.}
            \resumeItem{Added tagging and categorization features for resource management. Enhanced user organization and searchability by 50\% with intuitive UI design.}
            \resumeItem{Reduced page load time by 25\% and boosted overall performance.}
          \resumeItemListEnd
          

      \resumeProjectHeading
            {\textbf{Tic-Tac-Toe} $-$ \hrefWithoutArrow{https://dapper-bienenstitch-3880b8.netlify.app/}{\underline{Demo}} $|$ \hrefWithoutArrow{https://github.com/umesh550/tic-tac-toe}{\underline{Code}} }{\textbf{Tools:} HTML5, CSS3, TypeScript, MVC Architecture}
          \resumeItemListStart
            \resumeItem{Developed MVC-based browser game using TypeScript with real-time updates and persistent sessions. Utilized LocalStorage API for data storage and responsive UI design.}
            \resumeItem{Created cross-tab synchronization. Enabled seamless gameplay across multiple tabs with real-time state management.}
            \resumeItem{Leveraged TypeScript for type safety and better code maintainability. Reduced runtime errors by 30\% with object-oriented programming principles.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------VOLUNTEERING/EXTRACURRICULAR-------------
\section{Volunteering \& Extracurricular}
\resumeItemListStart
    \resumeItem{Organized college tech fests with 200+ students. Managed logistics, outreach, and promotion activities.}
    \resumeItem{Contributed to college cricket team success. Assisted with team coordination and strategy development.}
\resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Geethanjali Institute of Science and Technology}{Nellore, AP}
    {Bachelor of Technology in Electronics and Communication}{Aug 2019 -- May 2023}
  \resumeSubheading
    {Narayana Jr College}{Nellore, AP}
    {Class XII}{Aug 2017 -- May 2019}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=*, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Go, Python, JavaScript (ES6+), TypeScript, SQL, HTML5, CSS3} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Node.js, Express.js, Tailwind CSS} \\
     \textbf{Databases \& ORM}{: PostgreSQL, MongoDB, Redis, Prisma, Supabase} \\
     \textbf{Cloud \& DevOps}{: AWS (EC2, S3), Docker, CI/CD, GitHub Actions, Git, Version Control, Vercel} \\
     \textbf{Tools \& Platforms}{: VS Code, Postman, Figma, Linux, JWT, REST API} \\
     \textbf{Core Concepts}{: Data Structures, Algorithms, Object-Oriented Programming, API Design, Authentication}
     }}
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeItemListStart
    \resumeItem{\hrefWithoutArrow{https://media.geeksforgeeks.org/courses/certificates/83b5380337e445779d8bec9df86dc7b4.pdf}{Data Structures \& Algorithms $-$ GeeksforGeeks}}
    \resumeItem{\hrefWithoutArrow{https://drive.google.com/file/d/1zAgdQ--ppQRmWtNPaNEeFzaE2breL1zR/view?usp=sharing}{Frontend Developer (React) $-$ HackerRank}}
    \resumeItem{\hrefWithoutArrow{https://drive.google.com/file/d/1p8UQlg2GJg-SSlqVivx4N45oMRCu2p9A/view?usp=sharing}{JavaScript (Intermediate) $-$ HackerRank}}
    \resumeItem{\hrefWithoutArrow{https://www.credly.com/badges/415ebbd5-5b29-4661-987a-ac8866d76a17/public_url}{GitHub Foundations $-$ GitHub}}
    \resumeItem{\hrefWithoutArrow{https://drive.google.com/file/d/1T9rgtHr8c2eB3HyS8dRhQeAUYWzX7xXL/view?usp=sharing}{Build Responsive Real-World Websites with HTML and CSS $-$ Udemy}}
\resumeItemListEnd

\end{document}
