%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdfusetitle,hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}

\usepackage{fontawesome5}   % for icons
\usepackage{ifthen}     

%----------FONT OPTIONS----------
% Font options
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)

\definecolor{zinc600}{RGB}{82,82,91}
\definecolor{darkblue}{RGB}{0,0,139}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \\[2pt]
      \footnotesize#2 & \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}: #2}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Global list spacing and margins (flush-left bullets)
\setlist[itemize]{leftmargin=0pt,labelsep=0.6em,itemindent=0pt,labelindent=0pt}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0pt, label={}, itemsep=0.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=0pt, label={}, itemsep=1.7mm]}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}}

% Fix external-link icons in \href
\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{#2 \raisebox{.15ex}{\footnotesize \faExternalLink*}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\headerfontiii

%----------HEADING----------
\begin{center}
    {\Huge\textbf{UMESH TIRUVALLURU}}
    \vspace{2.5 mm} \\
    {\Large \textmd{Software Development Engineer}} 
    \vspace{2 mm} \\
    \normalsize
    \mbox{{\footnotesize\faMapMarker*}\hspace*{0.13cm}Nellore, Andhra Pradesh} \kern 0.5cm
    \mbox{\hrefWithoutArrow{mailto:tiruvalluruumesh@gmail.com}{{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}tiruvalluruumesh@gmail.com}} \kern 0.5cm
    \mbox{\hrefWithoutArrow{tel:+91-834-186-48-14}{{\footnotesize\faPhone*}\hspace*{0.13cm}+91 83418 64814}} \kern 0.5cm
    \mbox{\hrefWithoutArrow{https://www.umesh.tech/}{{\footnotesize\faLink}\hspace*{0.13cm}umesh.tech}} \kern 0.5cm
    \vspace{2 mm}
    \mbox{\hrefWithoutArrow{https://linkedin.com/in/umeshTiruvalluru}{{\footnotesize\faLinkedinIn}\hspace*{0.13cm}umeshTiruvalluru}} \kern 0.5cm
    \mbox{\hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru}{{\footnotesize\faGithub}\hspace*{0.13cm}Umesh-Tiruvalluru}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
      {Kinfocloud Tech Solution}{Bangalore, India}
      {Full Stack Developer Intern}{August 2024 - November 2024}
      \resumeItemListStart
        \resumeItem{Resolved 15+ critical production issues on client-facing web applications. Reduced page load times by 30\% and improved user experience.}
        \resumeItem{Built RESTful APIs using Node.js and MongoDB with authentication and data validation. Handled 1000+ daily API requests.}
        \resumeItem{Performed code reviews and implemented best practices. Used Git/GitHub for version control to improve code quality.}
        \resumeItem{Worked in Agile environment. Participated in sprint planning, daily standups, and retrospectives to deliver features on time.}
      \resumeItemListEnd 
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Geethanjal Institute of Science and Technology}{Nellore, India}
    {Bachelor of Technology in Electronics and Communication}{July 2019 - August 2023}
    \resumeItemListStart
      \resumeItem{CGPA: 7.07/10.00}
    \resumeItemListEnd
  \resumeSubheading
    {Narayana Jr College}{Nellore, India}
    {Pre-University Education}{June 2017 -- May 2019}
    \resumeItemListStart
      \resumeItem{CGPA: 9.7/10.00}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{CozyStay} $-$ \hrefWithoutArrow{https://linkbrain.onrender.com}{\underline{Demo}} $|$ \hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru/BookBnb}{\underline{Code}} }{Tools: Golang, PostgreSQL, Chi Router, Next.js, TypeScript, Tailwind CSS, Shadcn UI, Docker, JWT, REST API, AWS EC2, GitHub Actions}
    \resumeItemListStart
      \resumeItem{Built full-stack property booking platform using Go, Next.js, and TypeScript. Created scalable RESTful APIs with Chi router and JWT authentication for 500+ users.}
      \resumeItem{Implemented role-based access control (RBAC) with PostgreSQL. Created admin-only endpoints and protected sensitive operations using middleware authentication.}
      \resumeItem{Optimized Dockerfiles with multi-stage builds for backend and frontend. Reduced image sizes by 45\% and improved startup times by 35\%.}
      \resumeItem{Set up GitHub Actions CI/CD pipeline for automated builds and AWS EC2 deployment. Reduced manual deployment time by 60\%.}
      \resumeItem{Developed booking system with dynamic search, real-time availability checks, automated pricing, and cancellation workflows. Processed 200+ bookings.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Shortify} $-$ \hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru/shortify}{\underline{Code}} }{Tools: Java, Spring Boot, Maven, PostgreSQL, Spring Data JPA, REST API}
    \resumeItemListStart
      \resumeItem{Built production-ready URL shortening service using Spring Boot, PostgreSQL, and JPA. Implemented CRUD operations, URL redirection, and analytics for 1000+ URLs.}
      \resumeItem{Designed scalable database schema with unique short codes, access counters, and timestamps. Used PostgreSQL indexes to ensure data integrity and fast queries.}
      \resumeItem{Implemented business logic using Spring patterns. Generated Base62 short codes with uniqueness constraints and real-time usage statistics.}
      \resumeItem{Added input validation with Spring Validation and global exception handling. Improved API reliability by 40\% with better error responses.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{LinkBrain} $-$ \hrefWithoutArrow{https://linkbrain.onrender.com}{\underline{Demo}} $|$ \hrefWithoutArrow{https://github.com/Umesh-Tiruvalluru/LinkBrain}{\underline{Code}} }{Tools: React.js, React Query, Tailwind CSS, TypeScript, Node.js, Express.js, MongoDB, JWT, REST API}
    \resumeItemListStart
      \resumeItem{Built full-stack MERN application for organizing resources with user authentication. Grew to 50+ active users managing 500+ bookmarked resources.}
      \resumeItem{Implemented secure authentication using JWT tokens. Protected user actions and API endpoints with proper authorization.}
      \resumeItem{Added tagging and categorization features for resource management. Improved user organization and searchability by 50\%.}
      \resumeItem{Optimized database queries using MongoDB aggregation pipelines and React Query caching. Reduced page load time by 25\%.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {Java, Python, JavaScript (ES6+), TypeScript, Go, C/C++, SQL}
  \resumeSubItem{Frameworks \& Libraries:}
    {React.js, Next.js, Node.js, Express.js, Spring Boot, Tailwind CSS, JWT}
  \resumeSubItem{Database Systems:}
    {PostgreSQL, MongoDB, Redis, Database Design, Query Optimization}
  \resumeSubItem{Cloud \& DevOps:}
    {AWS (EC2, S3), Docker, CI/CD, GitHub Actions, Git, Version Control}
  \resumeSubItem{Testing \& Tools:}
    {Postman, API Testing, Figma, VS Code, Linux, Maven}
  \resumeSubItem{Core Concepts:}
    {Data Structures, Algorithms, Object-Oriented Programming, RESTful APIs, Microservices, Agile, SDLC}
\resumeHeadingSkillEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumePOR{}{\hrefWithoutArrow{https://www.credly.com/badges/415ebbd5-5b29-4661-987a-ac8866d76a17/public_url}{GitHub Foundations -- GitHub}}{}
  \resumePOR{}{\hrefWithoutArrow{https://media.geeksforgeeks.org/courses/certificates/83b5380337e445779d8bec9df86dc7b4.pdf}{Data Structures \& Algorithms -- GeeksforGeeks}}{}
  \resumePOR{}{\hrefWithoutArrow{https://drive.google.com/file/d/1zAgdQ--ppQRmWtNPaNEeFzaE2breL1zR/view?usp=sharing}{Frontend Developer (React) -- HackerRank}}{}
\resumeSubHeadingListEnd

\end{document}
